Security Audit of Safeplug

### 2014-02-20 w2sp/report.tex
added new image
Version table and software writing

\begin{figure*}[!b]
\centering
\subfloat[][Top of the board inside the Safeplug device.]{
  \includegraphics[width=.3\textwidth]{safeplug_listed_top}
  \label{fig:top}
}
\qquad
\subfloat[][Bottom of the Board inside the Safeplug device.]{
  \includegraphics[width=.3\textwidth]{safeplug_listed_bottom}
  \label{fig:bottom}
}
\caption{Safeplug circuit board after the teardown.}
\end{figure*}

@@

\subsection{Terms of Service}
\label{tos}
The Terms of Service (TOS) contains three main points of interest: TOS updates, open source licensing information, and software updates.

@@

\subsection{Tor Relay Node Option}
One of Safeplug's configurations is the use of the device as a Tor relay node in the Tor network.  When the device is initially setup, the default setting is to not use it as a relay node.

@@

\subsection{Software on the Safeplug}
The software installed by the activation process on the Safeplug (it is not on the box prior to the activation) is in \verb!/opt/xce! and includes lighttpd, privoxy, and tor.  Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [... while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.  Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removing ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.  Privoxy is also open source.  All three pieces of software appear to have default configuration files.  The fourth piece of software discovered on the device, which does not seem to be installed during the activation process is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.  The Safeplug uses its own configuration files to determine how these pieces of software are set up and used.

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=.4\textwidth]{settings}
  \caption{Settings page.}
  \label{fig:settings}
\end{figure}

@@

\begin{figure*}[htb]
\centering
\subfloat[][Web page before using Tor and ad-blocking.]{
  \includegraphics[width=.4\textwidth]{before}
  \label{fig:before}
}
\quad
\subfloat[][Webpage after using Tor and ad-blocking.]{
  \includegraphics[width=.4\textwidth]{after}
  \label{fig:after}
}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{funnygoogle}
  \caption{Google's response after trying to log in.}
  \label{fig:funnygoogle}
\end{figure}

@@

@@

>>>>

\begin{figure*}[!b]
\centering
\subfloat[][Top of the board inside the Safeplug device.]{
  \includegraphics[width=.3\textwidth]{safeplug_listed_top}
  \label{fig:top}
}
\qquad
\subfloat[][Bottom of the Board inside the Safeplug device.]{
  \includegraphics[width=.3\textwidth]{safeplug_hardware_new}
  \label{fig:bottom}
}
\caption{Safeplug circuit board after the teardown.}
\end{figure*}

@@

\subsection{Information Prior to Using the Device: Terms of Service}
\label{tos}
The Terms of Service (TOS) contains three main points of interest: TOS updates, open source licensing information, and software updates.

@@

\subsection{Tor Relay Node Option}
\label{port9001}
One of Safeplug's configurations is the use of the device as a Tor relay node in the Tor network.  When the device is initially setup, the default setting is to not use it as a relay node.

@@

\subsection{Software on the Safeplug}

\begin{center}
	\begin{tabular}{|c|c|c|}
	\hline
		Safeplug Software 	& Version 		& Date \\ \hline
		Linux Kernel				& 2.6.31.8 	& 2009 \\ \hline
		Lighttpd Web Server & 1.4.33			& 2013 \\ \hline
		Privoxy Proxy				& 3.0.21			& 2013 \\ \hline
		Tor Onion Routing		& 0.2.3.25		& 2012 \\ \hline
		Dropbear sshd				& v0.52			& 2008 \\ \hline
	\end{tabular}
\end{center}

The Safeplug runs version 2.6.31.8 of Arch Linux on an ARM architecture, which was produced at the end of 2009 and installed on 23 August 2011.  Unsurprising for its age, there are a number of network vulnerabilities for this version of the kernel - most of which seem to produce denial of service attacks if an adversary sends a particularly formed packet \cite{kernelcve}.  This is the same version of Linux that runs on Version 4 of PogoPlug's Mobile platform \cite{archforum}.

The software installed by the activation process on the Safeplug (it is not on the box prior to the activation) is in \verb!/opt/xce! and includes lighttpd, privoxy, and tor.  Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [... while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.  The version of lighttpd on the box is only one version away from being up to date, 1.4.33 which was released on 27 September 2013.  The current version of lighttpd, which has a number of security fixes, was released on 20 January 2014, after the Safeplug was purchased.  However, checking for an update from the Safeplug does not lead to any updated software installation, one of many cases of inattention to detail.

Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removing ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.  Privoxy is also open source.  The version on the device is 3.0.21, which is the most recent release.

The version of Tor is v0.2.3.25 which is from November 2012.  The current stable version of Tor is v0.2.4.20 from December 2013.  Unlike Lighttpd and Privoxy, the Safeplug does not contain the most up-to-date version of Tor from when it was released.

The fourth piece of software discovered on the device, which is not installed during the activation process and is in \verb!/usr/sbin! is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.  The Safeplug uses its own configuration files to determine how these pieces of software are set up and used.  The version of Dropbear on the Safeplug is v0.52 from 2008, which is extremely out of date.  Given the different location and installation methods, it seems likely that this was from the older Pogoplug device and is not designed to be updated in the same manner as the rest of the Safeplug software.

\subsection{Networking}
The lighttpd, Privoxy and Dropbear software give some indication of the networking services on the device.  We used \texttt{nmap} to scan the ports.  Before the activation of the Safeplug, only ports 80 and port 3333 are open.  After the activation, without the use of Tor turned on, ports 22 for SSH, port 80 for settings access and port 8080 for http-proxy are open.  When Tor is turned on as a relay, port 9001 tor-orport is opened as well.  This corresponds with the note on the settings page about Tor relays discussed in Section \ref{port9001} above.

@@

\begin{figure}[htb]
  \begin{center}
  \includegraphics[width=.4\textwidth]{settings}
  \caption{Settings page.}
  \label{fig:settings}
	\end{center}
\end{figure}

@@

\begin{figure*}[!b]
\centering
\subfloat[][Web page before using Tor and ad-blocking.]{
  \includegraphics[width=.3\textwidth]{before}
  \label{fig:before}
}
\quad
\subfloat[][Web page after using Tor and ad-blocking.]{
  \includegraphics[width=.3\textwidth]{after}
  \label{fig:after}
}
\caption{Application of Safeplug proxy settings.}
\end{figure*}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{funnygoogle}
  \caption{Google's response after trying to log in.}
  \label{fig:funnygoogle}
	\end{center}
\end{figure}

@@

\bibitem{archforum} Arch Linux ARM Forums. ``Installation on the Pogoplug Series 4.'' \url{http://archlinuxarm.org/forum/viewtopic.php?f=3&t=2284&start=14&sid=11c74c51b7bab241186a8341ba953095}

@@

\bibitem{kernelcve} Security Database. ``Linux Linux Kernel 2.6.13.8 CVE'' \url{http://www.security-database.com/cpe.php?detail=cpe:/o:linux:linux_kernel:2.6.31.8}
